CRUSE to Safe Cycling in Ireland

### 2023-10-10 paper.qmd
Add another reference

Although Dublin City has made progress, there are still many parts of the Fastest route network, and even some parts of the Balanced and Quietest route networks, that are not cycle friendly and which have high cycling potential.
According to a recent report, 71% of residents in the Dublin Metropolitan Area support "more cycle tracks along roads, physically separated from traffic and pedestrians".[^1]
The results for the Dublin area could help prioritise investment in cycling infrastructure in the city.

[^1]: https://www.nationaltransport.ie/wp-content/uploads/2022/05/220504-WACI22_DublinMetropolitanArea_v35_DIGITAL_v2.pdf

>>>>

Although Dublin City has made progress, there are still many parts of the Fastest route network, and even some parts of the Balanced and Quietest route networks, that are not cycle friendly and which have high cycling potential.
According to a recent report, 71% of residents in the Dublin Metropolitan Area support "more cycle tracks along roads, physically separated from traffic and pedestrians" [@walking2021].
The results for the Dublin area could help prioritise investment in cycling infrastructure in the city.
